### 2018-09-06 case_for_support.tex
Added new Gantt Chart

  \vspace{2mm}
  \noindent
  Our collaboration started in February, 2017, with a 12-month STFC Newton-funded project followed by a further 24-month Newton grant. For the Newton project, our team works with Thai graduate students to research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO). GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}. The primary {\it research} goals of our Newton project are to: (a) develop a data warehouse that is capable of storing large amounts of data that updated on a daily basis, yet is readily analysed at any time and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO. Our research in this area has been recognised as cutting edge within the field of data science, with two of our students winning awards for their presentations at two major international data science conferences (see attachments). With our Newton projects focussing on archiving and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.

@@

  \begin{itemize}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
    \item {\bf Thai AirAsia} is part of the AirAsia group, the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility. A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while waiting for the delivery of replacement parts. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement. AirAsia engineers will share their flight data with the students working on this project, and work with them to adapt our technologies to better predict when parts will require replacement.
    \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand. The business has grown rapidly over the past decade, and are now looking to expand into more locations. A problem they face when opening new stores is how to predict customer demographics, which has knock-on effects on how to stock the new store. Their aim is to work with a small group of students and researchers to research effective means to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
    \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand. Deevana use promotions to attract guests to their hotels. At present they use a scatter-gun approach to advertise these promotions, whereas they wish to investigate whether more targeted campaigns based on customer need can deliver better results. Deevana will work with our students to research how machine learning -- in particular clustering analysis -- could identify different types of customers and test which promotions are most effective at attracting different customer types.
    \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok. They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand. Biophics wishes to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance. This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
    \item {\bf OpenLandscape} is a provider of cloud computing infrastructure and services in Thailand. In order to grow, OpenLandscape needs to attract customers, but also be able to predict when those customers will place greatest load on their systems. OpenLandscape would like to work with our students to (a) analyse their customer database and usage logs to classify customers according to their usage type, and (b) analyse the usage logs of their hardware to predict those times when there is heaviest load on their systems.
  \end{itemize}
  Following the first twelve months of the project, we will hold another networking event to help attract more external partners to work with a new cohort of students.

  \vspace{2mm}
  \noindent
  By working closely with external partners, our team of researchers and trainers are gaining significant insights into the skills shortages experienced by Thai businesses. This makes our team extremely well-suited to providing highly relevant training to broader sections of Thai society beyond those that are able to attend university, particularly those already those already in full-time employment. To capitalise on this opportunity, we request funding to develop a distance-learning course in data science skills that are in high demand by Thai businesses. This will be achieved, in part, through a Massive Open Online Course (MOOC). We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps that they have identified within the Thai workforce, while also ensuring that the courses are accessible to current and potential employees. On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during that final 7 months of the project. The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems using our team's own data.

@@

  \noindent
  Over the 24-month period of the grant, we will (in broadly chronological order; see Gantt Chart):
  \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members and representatives from all our pre-identified external partners. At the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the first GCRF-funded project. Representatives from our external partners will be asked to describe their business/organisation and what they seek to achieve from the collaboration
  \item Each partner will be assigned a staff researcher as a main contact, who will also lead the supervision of a group of final-year project students. The role of the primary contact is to coordinate fortnightly meetings with the external partner to provide progress updates and receive feedback. Within the first three months of the project, the students will visit and work with each external user for at least 2 weeks to ensure they fully understand the data and problem.
  \item Around month 4 each team's will transition to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the external partners. During the fortnightly meetings the teams will demonstrate their solutions and encourage the client to suggest improvements.
  \item During month 7, we will host another meeting between UK and Thai team members and representatives from all external partners. This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified during the past six months, and revise the working plan for the rest of the projects. Plans will be made for further on-site visits and internships.
  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technnologies to meet our partners' needs. As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements. 
  \item By month ten, the team will deliver “beta versions” of our solutions. At this time, with the use of new virtual classroom at MFU, the team will train the end user on how to use the systems and collect any immediate feedback they may have. Following feedback, students will work on delivering the final products by month twelve.
  \item We will hold a networking event in month 12 to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships. This event will be attended by other potential partners to work with a new cohort of final-year students during months 13-24.
  \end{enumerate}

>>>>

  \vspace{2mm}
  \noindent
  Our collaboration started in February, 2017, with a 12-month STFC Newton project followed by a further 24-month Newton grant. For the Newton project, our team works with Thai graduate students to research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO). GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}. The primary {\it research} goals of our Newton project are to: (a) develop a data warehouse that is capable of storing large amounts of data that is updated on a daily basis, yet is readily analysed using complex algorithms and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO. Our research in this area has been recognised as cutting edge within the field of data science, with our students winning awards for their presentations at two major international data science conferences (see attachments). With our Newton projects focussing on storing and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.

@@

  \begin{itemize}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
    \item {\bf Thai AirAsia} is part of the AirAsia group, the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility. A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while waiting for the delivery of replacement parts. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement. AirAsia engineers will share their flight data with the students working on this project, and work with them to adapt our technologies to better predict when parts will require replacement.
    \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand. The business has grown rapidly over the past decade, and are now looking to expand into more locations. A problem they face when opening new stores is how to predict customer demographics, which has knock-on effects on how to stock the new store. Their aim is to work with a small group of students and researchers to research effective means to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
    \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand. Deevana use promotions to attract guests to their hotels. At present they use a scatter-gun approach to advertise these promotions, whereas they wish to investigate whether more targeted campaigns based on customer need can deliver better results. Deevana will work with our students to research how machine learning -- in particular clustering analysis -- could identify different types of customers and test which promotions are most effective at attracting different customer types.
    \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok. They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand. Biophics wishes to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance. This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
    \item {\bf OpenLandscape} is a provider of cloud computing infrastructure and services in Thailand. In order to grow, OpenLandscape needs to attract customers, but also be able to predict when those customers will place greatest load on their systems. OpenLandscape would like to work with our students to (a) analyse their customer database and usage logs to classify customers according to their usage type, and (b) analyse the usage logs of their hardware to predict those times when there is heaviest load on their systems.
  \end{itemize}
  Following the first twelve months of the project, we will hold another networking event to help attract more external partners to work with a new cohort of students. We have also budgetted for two Thai researchers to visit the UK twise during the project to help expand the project to include UK partners.

  \noindent
  By working closely with external partners, our team of researchers are gaining deep insights into the skills shortages experienced by Thai businesses. This makes our team extremely well-suited to providing highly relevant training to broader sections of Thai society beyond those that are able to attend university, including those already in full-time employment. To capitalise on this opportunity, we request funding to develop a distance-learning course to teach the data-handling skills that are in high demand by Thai businesses. This will be achieved, in part, through a Massive Open Online Course (MOOC). We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps they face and to ensure that the courses are accessible to current and potential employees. On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during the final seven months of the project. The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems based on using our team's own data.

@@

  \noindent
  Over the 24-month period of the grant, we will (in broadly chronological order; see Gantt Chart):
  \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members, students,and representatives from all our pre-identified external partners. At the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the first GCRF-funded project. Representatives from our external partners will be asked to describe their business/organisation and what they seek to achieve from the collaboration
  \item Each partner will be assigned a staff researcher as a main contact, who will also lead the supervision of a group of final-year project students. The role of the primary contact is to coordinate fortnightly discussions with the external partner to provide progress updates and receive feedback. Within the first three months of the project, the students will visit and work with each external user for at least two weeks to ensure they fully understand the data and problem.
  \item Around month four each team will transition to the implementation phase by focusing on adapting our technology and techniques to the needs of the external partners. During the fortnightly meetings the teams will demonstrate their solutions and encourage the client to suggest improvements.
  \item During month seven, we will host another meeting between UK and Thai team members and representatives from all external partners. This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified during the past six months, and revise the working plan for the rest of the projects. Plans will be made for further on-site visits and internships. Around this time, we will also start work on developing the MOOC, following consultation with our external partners.
  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technnologies to meet our partners' needs. As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements. 
  \item By month ten, the team will deliver “beta versions” of our solutions. At this time, with the use of new virtual classroom at MFU, the team will train the end user on how to use the systems and collect any immediate feedback they may have. Following feedback, students will work on delivering the final products by month twelve.
  \item We will hold a networking event in month 12 to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships. This event will be attended by other potential partners to work with a new cohort of final-year students during months 13-24.
  \item The next twelve months of the partner-focussed part of the project will follow a similar schedule as the first twelve months, but with a new cohort of students and new external partners. Around month twelve, we will broadcast our MOOC
  \end{enumerate}
